\Large{Weight-at-length of the invasive lionfish \textit{Pterois volitans} (Actinopterygii, Scorpaenidae) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}

### 2017-09-29 Manuscript.tex
Manuscript finalized

\setlength{\droptitle}{-2em}
  \title{\Large{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
\subtitle{\textbf{Running title}: Allometric growth of Pterois volitans}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers

@@

Juan Carlos VILLASEÑOR-DERBEZ\textsuperscript{1}

@@

\textbf{Background.} Lionfish (\emph{Pterois volitans/miles}) are an
invasive species in the North-Western Atlantic and the Caribbean. In
order to better manage the invasion, inform lionfish removal programs,
predict their possible impacts, and estimate biomass available for
harvest, we must be able to accurately estimate their total biomass.
Previous work has identified that lionfish age-at-length relationships
are spatially variable across the invasion range. This work had two main
objectives: i) compare length-weight relationships of the invasive
lionfish through the invasion range; and ii) Report the length-weight
frequency for lionfish in the Central Meixcan Caribbean.

\textbf{Materials and methods.} A total of 13 length-weight
relationships reported in eight peer-reviewed studies and FishBase were
used to calculate expected biomass of organisms (n = 109) sampled from
the Central Mexican Caribbean, whose Total Length (TL) and Total Weight
(TW) were known. For each length-weight relationship,
expected-to-observed weight ratio was calculated for each organism.
Differences in mean expected-to-observed weight ratios were tested with
a one-way ANOVA; Tukey's HSD was used as a post-hoc test to identify
groups of non-statistically significant differences. Additionally, the
length-weight relationship of the 109 organisms was calculated. Total
Length (TL) and Total weight (TW) were log10-transformed to fit a linear
model describing the linearized length-weight relationship. The model
was fit using Ordinary Least Squares and Heteroskedastik-robust standard
errors were computed.

\textbf{Results.} Expected-to-observed weight ratios ranged from 0.44 to
3.51, and dfferences in weight-at-length were spatially consistent. For
a given length, parameters from the Caribbean yielded lower weights than
those from the Gulf of Mexico and Atlantic, indicating that
weight-at-length is spatially variable. This study also reports a new
pair of length-weight parameters
(\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
Central Mexican Caribbean.

\textbf{Conclusion.} The large differences between observed and expected
biomass when using parameters from other locations highlights the
importance of using site-specific parameters to estimate biomass from
length observations. Findings from this work can aid managers and
decision makers to better select length-weight parameters when these are
not available for their region of interest.

\textbf{Key words}\\
lionfish, Pterois volitans, length-weight relationship, allometric
growth, Mexico

@@

\section{INTRODUCTION}\label{introduction}

@@

\section{MATERIALS AND METHODS}\label{materials-and-methods}

\textbf{Area of study.} The study took place off the coasts of Playa del
Carmen, in the Mexican Caribbean (\textbf{Fig. 1}). The region
represents the northernmost section of the Mesoamerican Barrier Reef
System (Ruiz-Zarate \& Arias-Gonzalez, 2004). Coral reefs and mangroves
are locally important habitats that represent important sources of
income in terms of extractive (\emph{e.g.} recreational fishing) and
non-extractive (\emph{e.g.} SCUBA diving) activities related to tourism,
the main source of income to the local economy (Murray, 2007).

@@

\textbf{Fish sampling.} A total of 33 SCUBA immersions were performed in
10 sampling sites along the coast in 2010 (Fig. 1, Table 1). Sampling
locations included wall and carpet reefs at depths between 5.7 m and
38.1 m. All observed organisms (n = 109) were collected using hand nets
and numbered collection bottles. The use of hand nets prevented any
weight loss due to bleeding and allowed a better representation of small
sizes, often ignored due to gear selectivity when spearing. Organisms
were euthanized and frozen within 30 minutes of completing the dive and
stored for posterior analysis. Total Length (TL; mm) and Total Weight
(TW; gr) were recorded for all organisms.

\textbf{Data analysis.} The weight at length relationship between the
observed variables is described by the allometric growth function:

@@

\section{RESULTS}\label{results}

@@

\textbf{Length-weight relationship.} The model adjusted to eq. 3
estimated the coefficient values at \(b = 3.2347391\) and
\(c = -5.4940866\). Thus, TW (gr) can be calculated from TL (mm) as a
linear equation:
\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\), or its
exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
The intercept (\(c\)) and slope \((b)\) were significantly different
from zero (\(t(107) = -66.17; p<0.01\) and \(t(107) = 83.24; p<0.01\),
respectively), rejecting the null hypothesis of no change. Additionally,
the allometric factor (\(b\)) was significantly different from the value
of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)), indicating
that lionfish present allometric growth. More information on model fit
and confidence intervals for the estimated coefficients is presented in
Table 2. The relationship between Total Length and Total Weight is
presented in Figure 3.

\textbf{Comparison of allometric parameters.} From the eight
peer-reviewed studies including information on growth parameters for
\emph{P. volitans} and Fishbase (Froese \& Pauly, 2016), 13 parameters
were identified (Table 3). Two studies (Fogg et al., 2013;
Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and pooled
parameters, while the rest presented pooled results. The smallest
coefficient of determination was presented by Chin, Aiken \& Buddo
(2016) with \(R^2 = 0.8715\), while Sabido-Itza et al. (2016) reported
the highest value at \(R^2 = 0.9907\). Reviewed studies presented
information for organisms obtained at depths between 0.5 and 57 m. Two
studies (Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken \& Buddo,
2016) explicitly stated that their organisms were sampled with pole
spears. Five studies (Barbour et al., 2011; Fogg et al., 2013; Edwards,
Frazer \& Jacoby, 2014; Sandel et al., 2015; Sabido-Itza et al., 2016)
mentioned that some of their organisms were obtained with pole spears
(or other type of harpoon). A single study (de Leon et al., 2013) did
not specify how organisms were sampled.

@@

@@

\section{DISCUSSION}\label{discussion}

@@

\section{AKNOWLEDGEMENTES}\label{aknowledgementes}

@@

\section{REFERENCES}\label{references}

@@

\section{TABLES}\label{tables}

Table 1: Coordinates, minimum, maximum and mean depth (m), and number of
samples for each location.

\begin{longtable}[]{@{}llllllr@{}}
\toprule
Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
n\tabularnewline
\midrule
\endhead
Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\tabularnewline
Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\tabularnewline
Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\tabularnewline
Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\tabularnewline
Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\tabularnewline
Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\tabularnewline
Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\tabularnewline
Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\tabularnewline
Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\tabularnewline
Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\tabularnewline
Total & & & 5.7 & 38.1 & 18.6 & 109\tabularnewline
\bottomrule
\end{longtable}

Table 2: Regression table for the linear model fit between
log10-transformed Total Weight (dependent variable) and Total Length
(independent variable). Numbers in parentheses next to coefficient
estimates indicate heteroskedastic-robust standard errors. The asterisks
(*) indicate the statistical significance. 95\% Confidence intervals are
provided for each parameter.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & log10(TW) \\ 
\hline \\[-1.8ex] 
 c & $-$5.494 (0.083)$^{***}$ \\ 
  b & 3.235 (0.039)$^{***}$ \\ 
 \hline \\[-1.8ex] 
95\% CI for c & (-5.657--5.331) \\ 
85\% CI for b & (3.159-3.311) \\ 
F Statistic & 6928.67*** (df = 1; 107) \\ 
Observations & 109 \\ 
Adjusted R$^{2}$ & 0.976 \\ 
Residual Std. Error & 0.096 (df = 107) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Table 3: Summary of 13 allometric growth parameters available for
lionfish in the invaded range from eight peer-reviewed papers, Fishbase
(Froese \& Pauly, 2016), and this study. All parameters have been
adjusted to convert from millimeters to grams. n = Sample size, a =
scaling parameter for eq. 1, c = y-intercept for eq. 3, b = exponent or
slope for eq. 1 or eq. 3, respectively. The R\textsuperscript{2} column
indicates reported model fit. mDepth and MDepth indicate minimum and
maximum depths (m), respectively, at which organisms were sampled. The
Spear column indicates if the study collected organisms with pole
spears. An asterisk (*) indicates that some portion of organisms were
sampled with pole spears. 1 = Aguilar-Perera \& Quijano-Puerto (2016), 2
= Sandel et al. (2015), 3 = Chin, Aiken \& Buddo (2016), 4 = Barbour et
al. (2011), 5 = de Leon et al. (2013), 6 = Fogg et al. (2013), 7 =
Edwards, Frazer \& Jacoby (2014), 8 = Sabido-Itza et al. (2016), 9 =
Froese \& Pauly (2016), 10 = This study.

\begin{table}[!h]
\centering
\resizebox{\linewidth}{!}{\begin{tabular}{rlllrrrllll}
\toprule
Reference & Region & Sex & a & c & b & R2 & n & mDepth & MDepth & Spear\\
\midrule
1 & Arrecife Alacranes, Mexico & Both & 472 & 0 & -5.5400 & 3 & 0.95 & 5 & 20 & Yes\\
1 & Arrecife Alacranes, Mexico & Female & 67 & 0 & -5.9300 & 3 & 0.95 & 5 & 20 & Yes\\
1 & Arrecife Alacranes, Mexico & Male & 59 & 0 & -5.3800 & 3 & 0.95 & 5 & 20 & Yes\\
2 & Southern Caribbean Coast of Costa Rica & Both & 458 & 0 & -4.4400 & 3 & - & - & - & Yes*\\
3 & Discovery Bay, Jamaica & Both & 419 & 0 & -4.5600 & 3 & 0.8715 & 18.3 & 18.3 & Yes\\
\addlinespace
4 & North Carolina & Both & 774 & 0 & -4.5391 & 3 & - & 27 & 45 & Yes*\\
5 & Bonaire & Both & 1450 & 0 & -4.6411 & 3 & 0.96 & - & - & NA\\
6 & Northern Gulf of Mexico & Both & 582 & 0 & -5.8600 & 3 & 0.99 & - & - & Yes*\\
6 & Northern Gulf of Mexico & Male & 119 & 0 & -5.5700 & 3 & 0.97 & - & - & Yes*\\
6 & Northern Gulf of Mexico & Female & 115 & 0 & -5.1700 & 3 & 0.94 & - & - & Yes*\\
\addlinespace
7 & Little Cayman & Both & 1887 & 0 & -5.5229 & 3 & 0.97 & 15 & 30 & Yes*\\
8 & Parque Nacional Arrecifes de Xcalak, Mexico & Both & 2143 & 0 & -5.2828 & 3 & 0.9907 & 0.5 & 57 & Yes*\\
9 & NA & Both & NA & 0 & -5.0293 & 3 & - & - & - & NA\\
10 & Puerto Aventuras, Mexico & Both & 109 & 0 & -5.4941 & 3 & 0.9766 & 5.7 & 38.1 & No\\
\bottomrule
\end{tabular}}
\end{table}

\section{Figures}\label{figures}

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{Map of the study area. The black inset on the left (Yucatan
Peninsula) indicates the location where study sites are distributed. On
the right, circular markers indicate sampling sites and the black
romboid indicates location of Puerto Aventuras, Mexico.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{Kernell density plots for a) Total length (mm) and b) Total
weight (gr) for 109 lionfish sampled in the central Mexican Caribbean.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{Length-weight relationship for 109 lionfish sampled in the
central Mexican Caribbean. Points indicate samples, solid line indicates
curve of best fit.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{Length-weight relationships (n = 14) for eight studies, this
study, and Fishbase. Colors indicate studies from which the parameters
were extracted. Solid lines indicate that the fit was performed for
males and females pooled together. Dotted lines indicate that the
regression was performed on females, and dashed lines indicate it was
performed for males.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{. Box and whiskers plot showing the distribution of predicted
to observed biomass ratios for 14 pairs of allometric parameters. Lines
indicate median values, circles indicate mean values, notches represent
95\% confidence intervals arround the median, lower and upper hinges
correspond to the first and third quartiles, whiskers extend to the
largest and lowes values within 1.5 inter-quartile range of the hinge,
small points represent outliers further away than the whiskers. Like
letters indicate values that do not differ significantly (Tukey's HSD; p
\textless{} 0.05).}
\end{figure}

>>>>

\setlength{\droptitle}{-2em}
  \title{\Large{Weight-at-length of the invasive lionfish \textit{Pterois volitans} (Actinopterygii, Scorpaenidae) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
\subtitle{\textbf{Running title}: Length-Weight relationships of lionfish}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{setspace}
\doublespacing

@@

Juan Carlos Villaseñor-Derbez\textsuperscript{1}

@@

\textbf{Abstract}

Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
North-Western Atlantic and the Caribbean. In order to better manage the
invasion, inform lionfish removal programs, and estimate biomass
available for harvest, we must be able to accurately estimate their
total biomass, frequently from length observations. This work compares
length-weight relationships of the invasive lionfish through the
invasion range and reports the length--weight relationship for lionfish
in the Central Mexican Caribbean. A review of 13 length--weight
relationships reported in eight peer-reviewed studies and FishBase is
provided. These parameters were used to identify spatial variation in
weight-at-length. For a given length, parameters from the Caribbean
yielded lower weights than those from the Gulf of Mexico and Atlantic,
indicating that weight-at-length is spatially variable. This highlights
the importance of using site-specific parameters to estimate biomass
from length observations. This study also reports a new pair of
length-weight parameters (\(a = 3.2056\times 10^{-6}; b = 3.235\)) for
organisms sampled in the Central Mexican Caribbean. Findings from this
work can aid managers and decision makers to better select length-weight
parameters when these are not available for their region of interest.

\textbf{Resumen}

El pez león (\emph{Pterois volitans/miles}) es una especie invasora en
el Atlántico Noroeste y el Mar Caribe. Para tener un mejor manejo de la
invasión, informar programas de remoción y estimar la biomasa disponible
para aprovechamiento, debemos ser capaces de estimar la biomasa
disponible con presisión, frecuentemente a partir de observaciones de
tallas. Este trabajo compara la relación longitud--peso del pez león a
través del rango de invasión, y reporta un nuevo par de parámetros de
crecimiento alométrico para la zona central del Caribe Mexicano. El
trabajo presenta revisión de 13 relaciones longitud--peso reportadas
reportadas en ocho estudios publicados en revistas arbitradas y
FishBase. Para una misma talla, los parámetros del Caribe indican un
mejor peso que los parámetros del Golfo de México y el Atlántico,
indicando una variabilidad espacial en la relación longitud peso. Esta
variabilidad resalta la importancia de utilizar parámetros específicos a
un sitio al estimar biomasa a partir de observaciones de tallas. Este
estudio también reporta una nueva relación longitud--peso
(\(a = 3.2056\times 10^{-6}; b = 3.235\)) para organismos muestreados en
la costa central del Caribe Mexicano. Los resultados de este trabajo
pueden ayudar a tomadores de decisiones en la selección de relaciones
longitud-peso cuando éstas no están disponibles para su zona de interés.

\textbf{Key words}\\
biometry, invasive species, spatial variability, allometric growth,
Mexico

@@

\section{Introduction}\label{introduction}

@@

\section{Materials and Methods}\label{materials-and-methods}

\emph{Area of study}

The study took place off the coasts of Playa del Carmen, in the Mexican
Caribbean (\textbf{Fig. 1}). The region represents the northernmost
section of the Mesoamerican Barrier Reef System (Ruiz-Zarate \&
Arias-Gonzalez, 2004). Coral reefs and mangroves are locally important
habitats that represent important sources of income in terms of
extractive (\emph{e.g.} recreational fishing) and non-extractive
(\emph{e.g.} SCUBA diving) activities related to tourism, the main
source of income to the local economy (Murray, 2007).

@@

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/create map-1.pdf}
\caption{Map of the study area. The black inset on the left (Yucatan
Peninsula) indicates the location where study sites are distributed. On
the right, circular markers indicate sampling sites and the black
romboid indicates location of Puerto Aventuras, Mexico.}
\end{figure}

\emph{Fish sampling}

A total of 33 SCUBA immersions were performed in 10 sampling sites along
the coast in 2010 (Fig. 1, Table I). Sampling locations included wall
and carpet reefs at depths between 5.7 m and 38.1 m. All observed
organisms (n = 109) were collected using hand nets and numbered
collection bottles. The use of hand nets prevented any weight loss due
to bleeding and allowed a better representation of small sizes, often
ignored due to gear selectivity when spearing. Organisms were euthanized
and frozen within 30 minutes of completing the dive and stored for
posterior analysis. Total Length (TL; mm) and Total Weight (TW; gr) were
recorded for all organisms.

\begin{longtable}[]{@{}llllllr@{}}
\caption{Coordinates, minimum, maximum and mean depth (m), and number of
samples for each location.}\tabularnewline
\toprule
Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
n\tabularnewline
\midrule
\endfirsthead
\toprule
Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
n\tabularnewline
\midrule
\endhead
Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\tabularnewline
Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\tabularnewline
Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\tabularnewline
Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\tabularnewline
Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\tabularnewline
Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\tabularnewline
Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\tabularnewline
Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\tabularnewline
Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\tabularnewline
Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\tabularnewline
Total & & & 5.7 & 38.1 & 18.6 & 109\tabularnewline
\bottomrule
\end{longtable}

\emph{Data analysis}

The weight at length relationship between the observed variables is
described by the allometric growth function:

@@

\section{Results}\label{results}

@@

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/histogram figures-1.pdf}
\caption{Kernell density plots for a) Total length (mm) and b) Total
weight (gr) for 109 lionfish sampled in the central Mexican Caribbean.}
\end{figure}

\emph{Length-weight relationship}

The model adjusted to eq. 3 estimated the coefficient values at
\(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
calculated from TL (mm) as a linear equation:
\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\), or its
exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
The intercept (\(c\)) and slope \((b)\) were significantly different
from zero (\(t(107) = -66.17; p<0.01\) and \(t(107) = 83.24; p<0.01\),
respectively), rejecting the null hypothesis of no change. Additionally,
the allometric factor (\(b\)) was significantly different from the value
of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)), indicating
that lionfish present allometric growth. More information on model fit
and confidence intervals for the estimated coefficients is presented in
Table II. The relationship between Total Length and Total Weight is
presented in Figure 3.

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/scatter plot-1.pdf}
\caption{Length-weight relationship for 109 lionfish sampled in the
central Mexican Caribbean. Points indicate samples, solid line indicates
curve of best fit.}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable). Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & log10(TW) \\ 
\hline \\[-1.8ex] 
 c & $-$5.494 (0.083)$^{***}$ \\ 
  b & 3.235 (0.039)$^{***}$ \\ 
 \hline \\[-1.8ex] 
95\% CI for c & (-5.657--5.331) \\ 
85\% CI for b & (3.159-3.311) \\ 
F Statistic & 6928.67*** (df = 1; 107) \\ 
Observations & 109 \\ 
Adjusted R$^{2}$ & 0.976 \\ 
Residual Std. Error & 0.096 (df = 107) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\emph{Comparison of allometric parameters}

From the eight peer-reviewed studies including information on growth
parameters for \emph{P. volitans} and Fishbase (Froese \& Pauly, 2016),
13 parameters were identified (Table III). Two studies (Fogg et al.,
2013; Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and
pooled parameters, while the rest presented pooled results. The smallest
coefficient of determination was presented by Chin, Aiken \& Buddo
(2016) with \(R^2 = 0.8715\), while Sabido-Itza et al. (2016) reported
the highest value at \(R^2 = 0.9907\). Reviewed studies presented
information for organisms obtained at depths between 0.5 and 57 m. Two
studies (Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken \& Buddo,
2016) explicitly stated that their organisms were sampled with pole
spears. Five studies (Barbour et al., 2011; Fogg et al., 2013; Edwards,
Frazer \& Jacoby, 2014; Sandel et al., 2015; Sabido-Itza et al., 2016)
mentioned that some of their organisms were obtained with pole spears
(or other type of harpoon). A single study (de Leon et al., 2013) did
not specify how organisms were sampled.

@@

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/review plots-1.pdf}
\caption{Length-weight relationships (n = 14) for eight studies, this
study, and Fishbase. Colors indicate studies from which the parameters
were extracted. Solid lines indicate that the fit was performed for
males and females pooled together. Dotted lines indicate that the
regression was performed on females, and dashed lines indicate it was
performed for males.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/plot comparing predictions-1.pdf}
\caption{. Box and whiskers plot showing the distribution of predicted
to observed biomass ratios for 14 pairs of allometric parameters. Lines
indicate median values, circles indicate mean values, notches represent
95\% confidence intervals arround the median, lower and upper hinges
correspond to the first and third quartiles, whiskers extend to the
largest and lowes values within 1.5 inter-quartile range of the hinge,
small points represent outliers further away than the whiskers. Like
letters indicate values that do not differ significantly (Tukey's HSD; p
\textless{} 0.05).}
\end{figure}

\section{Discussion}\label{discussion}

@@

\section{Aknowledgements}\label{aknowledgements}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

@@
